% You insert your abstract in the space below.


This work develops a globally convergent, data driven algorithm for estimating the Lyapunov exponents of a dynamical system.
This work rigorously tests our algorithm with two dynamical systems: The Lorenz equation and the Rossler equation. Additionally
the algorithm is used to approximate the Lyapunov exponents of two additional dynamical systems, the Chua equation, and
the Li equation \textit{Li et al.} \cite{item:6}.
The time series used as data points for the dynamical system was obtained
by numerical integration with the fourth-order Runge-Kutta scheme. Our algorithm then interpolates the time series
using radial basis functions. Three basic functions\texttwelveudash Gaussian, multiquadrics, and inverse\texttwelveudash
were tested using our algorithm. The shape parameter of the basic function was optimized using an algorithm
developed by \textit{Rippa} \cite{item:3}.
Our interpolation algorithm is used to produce a numerical approximation of the given dynamical system's Jacobian.
The Lyapunov exponents of the system are calculated by performing a QR-decomposition on the Jacobian approximation. We conducted
several trials with Lorenz and Rossler by varying the simulation parameters $t$, $dt$, and nearest neighbors.
Our trials provided good approximations of the Lorenz Lyapunov exponents except for two trials where $t=90$ and one where $dt=0.1$.
Our algorithm also produced good approximations of the Lyapunov exponents for the Chua and Li equations. However, the
algorithm struggled providing accurate approximations of the minimal Lyapunov exponent for Rossler but provided
accurate approximations for Rossler's maximal Lyapunov exponenent.


